Deep Reinforcement Learning for Conservation Decisions

### 2022-06-01 manuscript/manuscript.Rmd
Adding training details in results

We provide two examples that illustrate the application and potential of deep RL to ecological and conservation problems, highlighting both the potential and the inherent challenges.
Annotated code for these examples may be found in Appendix B and at <https://github.com/boettiger-lab/rl-intro>.

>>>>

We provide two examples that illustrate the application and potential of deep RL to ecological and conservation problems, highlighting both the potential and the inherent challenges.
Annotated code for these examples may be found in Appendix B and at <https://github.com/boettiger-lab/rl-intro>.
All algorithms were run on an NVIDIA Quadro RTX 8000 GPU.
The training  budget for the fishing scenario was 300K timesteps (3K runs, taking about 25 minutes).
Tipping point training budget was 3M timesteps (6K runs, taking around 3 hours).
Precise run times vary with machine load and algorithm.
Software details and hyperparameters are provided in the associated GitHub repo.
Hyperparameter tuning typically required 100s of training runs using both Optuna, a python-based hyperparameter optimization library, and manual adjustments.
